The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-27 paper/ms.tex
globular cluster metallicity?

\subsubsection{Chemical Composition}
\label{chemical}
The chemical compositions for each star were measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Na, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families. This was done to asses the Galactic populations from which these stars are drawn from. The first thing to note is that the metallicity, which are tabulated in Table~\ref{stellar_props}, are to high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be considered drawn from the Galactic halo, whose peak metallicity is around --1.20 \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge. These alone allow us to predict that theses stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\
{\bf $\alpha$ elements:}\\
\begin{figure*}
\noindent\includegraphics[width=\textwidth,keepaspectratio]{Pope_spectra_alphaele.pdf}

>>>>

\subsubsection{Chemical Composition}
\label{chemical}
The chemical compositions for each star were measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Na, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families. This was done to asses the Galactic populations from which these stars are drawn. The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be considered drawn from the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge. These alone allow us to predict that theses stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\
{\bf $\alpha$ elements:}\\
\begin{figure*}
\noindent\includegraphics[width=\textwidth,keepaspectratio]{Pope_spectra_alphaele.pdf}
